---
title: "116th Congress Tweet Dataset"
subtitle: "Quality Assessment Report"
author: "Ben Burnley"
date: "October 16, 2023"
format: 
  html:
    self-contained: true
message: false
---

# Introduction 
This document contains the data quality checks I performed to guarantee the data did not have large amounts of missingness or other issues. 



```{r}
#| echo: false
#| message: false
# libraries 
library(tidyverse)
library(lubridate)
library(kableExtra)
# load in data 
load("data/congress_116.Rdata")
# theme 
my_theme = theme_minimal()+
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(face = "italic")
  )
```


# 116th Congress 

### Date 
```{r}
#| include: false
class(congress_116$date)
length(unique(congress_116$date))
sum(is.na(congress_116$date))
```

The date column is formatted correctly and contains the correct amount of days from the time period of interest: 731 days, 365 in 2019 and 366 in 2020. There do not seem to be any discrepancies in the data. The plot below shows the total number of tweets per day across the two years of study.

```{r}
#| echo: false
#| message: false
congress_116 %>% 
  group_by(date) %>% 
  summarize(n = n()) %>% 
  ggplot(aes(date, n))+
  geom_point(alpha = 0.5)+
  geom_smooth(color = "red", se = F)+
  labs(
    title = "Total Tweets Per Day",
    x = "Day",
    y = "Count of Tweets"
  )+
  my_theme
```

### Time 
```{r}
#| include: false
# class of variable 
class(congress_116$time)
# percent of data that is missing time of tweet
sum(!is.finite(congress_116$time))/nrow(congress_116) 
```

About 2% of the data is missing a time recorded. This is not a parsing error, the underlying data is missing a time. 

```{r}
#| echo: false
#| message: false

congress_116 %>% 
  group_by(date) %>% 
  summarize(finites = sum(!is.finite(time)), tweets = n()) %>% 
  ggplot()+
  geom_line(aes(date, finites))+
  geom_line(aes(date, tweets), color = "red", alpha = 0.2)+
  labs(
    title = "Missingness Across Sample",
    subtitle = "Total Tweets in Red, Tweets with Missing Time in Black",
    x = "Date",
    y = "Count"
  )+
  my_theme
```
```{r}
#| echo: false
#| message: false

# how many account have missingness 
congress_116 %>% 
  group_by(username) %>% 
  summarize(total = n(), missing = sum(!is.finite(time)), pct_missing = missing/total) %>% 
  arrange(desc(pct_missing)) %>% 
  ggplot(aes(pct_missing)) +
  geom_histogram(fill = "red")+
  theme_minimal()+
  labs(
    title = "Percent Missing by Account",
    x = "Percent Missing",
    y = "Number of Accounts"
  )
```
Missingness is associate with account. With the exception of 3 accounts, time is either 100% present or missing. Path forward may be to separate out these accounts for analyses to see if they are impacting results. 

### Username 
```{r}
#| include: false
class(congress_116$username)
length(unique(congress_116$username))
sum(is.na(congress_116$username))
```

Usernames are represented by the unique character string associated with the account. There are 2200 unique user names in the data set. There is no missingness present in this variable. The table below displays the top 10 usernames by total tweets. 
```{r}
#| echo: false
x1 = congress_116 %>% 
  group_by(username) %>% 
  summarize(total_tweets = n()) %>% 
  arrange(desc(total_tweets)) %>% 
  head(10)

kable(x1, col.names = c("Username", "Total # of Tweets"))
```

### Name 
```{r}
#| include: false 

class(congress_116$name)
sum(is.na(congress_116$name))
sum(is.na(congress_116$name))/nrow(congress_116)
```

The name variable contains the account's display name at the time of scraping. This is a character string the may differ from the actual username of the account. About 2% of the data has missingness in this column. The top accounts, by total tweets, are shown below. These match with the usernames shown above. 

```{r}
#| echo: false 

congress_116 %>% 
  filter(!is.na(name)) %>% 
  group_by(name) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  kable(col.names = c("Name", "Total # of Tweets"))
  
```

### Language 
```{r}
#| include: false
class(congress_116$language)
sum(is.na(congress_116$language))
sum(is.na(congress_116$language))/nrow(congress_116)
```

